Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-01-31 automatica/paper.tex
overall paper

@@

As discussed in Section~\ref{sec:errors}, 
the considered models must account for finite precision arithmetic semantics deriving from several sources: 
we formally bound the numerical error introduced by the finite precision representation of the plant (and its operations), 
and precisely model the behaviour introduced by the ADC/DAC conversions, 
as well as the behaviour of the limited-precision arithmetic used by the controller.

Technically, we employ interval arithmetic to bound the error introduced by the finite precision plant, 
and we use bounded model checking to precisely model the semantics of finite precision arithmetic introduced by the ADC/DAC and the finite precision controller.

\subsection{Bit-precise symbolic model checking}
As described in Section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker to synthesise and verify candidate controllers. 
CBMC manipulates precisely the fixed- or floating-point arithmetic used in the controller, 
as well as the ADC/DAC conversions, 
according to the IEEE standards.

\subsection{Interval arithmetic for errors in the numerical representation}

We use finite precision arithmetic to model the plant. 
This is an approximation that speeds up each CEGIS iteration, 
however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a plant expressed over real numbers.  
In this stage, we represent the plant using double-precision floating-point numbers 
and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
We employ a compositional numerical library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
We check that the controller is safe starting from each vertex of the set of initial states,  
and show that this is sufficient to prove safety from any state in this set (see Theorem~\ref{th:safety}). %\note{add forward reference to proof.}

>>>>

\note{throughout the article, we mix the notions of system, plant, and model. 
I propose to clarify throughout as follows: \\ 
we do not use the term plant (eliminate from text). \\ 
we have an underlying physical/real/actual system. \\ 
we have an analogue model of it (1), with continuous variables and continuous time. \\ 
we discretise time, obtain the reference model for this article (2).  \\ 
we define specs and properties over this discrete-time model. and we synthesise controllers $u_k$ (not $u(t)$) on it. 
}

@@

As discussed in Section~\ref{sec:errors}, 
the considered models must account for the semantics of finite-precision arithmetic, 
deriving from several sources: 
we formally bound the numerical error introduced by the finite precision representation of the plant (and its operations), 
and precisely model the behaviour introduced by the ADC/DAC conversions, 
as well as the behaviour of the limited-precision arithmetic used by the controller.

Technically, we employ interval arithmetic to bound the error introduced by the finite-precision plant model, 
and we use bounded model checking to precisely model the semantics of finite-precision arithmetic, 
as introduced by the ADC/DAC blocks and by the finite-precision controller.

\subsection{Bit-precise bounded model checking}

As described in Section~\ref{sec:BMC}, we use CBMC, a bit-precise bounded model checker, 
to synthesise and verify candidate controllers. 
CBMC manipulates precisely the fixed- or floating-point arithmetic used in the controller, 
as well as the ADC/DAC conversions, according to the IEEE standards.

\subsection{Interval arithmetic for errors in numerical representations}

We use finite-precision arithmetic to model the plant. 
This is an approximation that speeds up each CEGIS iteration, 
however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a plant expressed over real numbers.  
In this stage, we represent the plant using double-precision floating-point numbers 
and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
We employ a compositional numerical library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
We check that the controller is safe starting from each vertex of the set of initial states,  
and show that this is sufficient to prove safety from any state in this set (see Theorem~\ref{th:safety}). %\note{add forward reference to proof.}
